Pillar 1 - Sequential Pattern Mining

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
update edit_rules

    # separate rule
    mutate(
      rule = str_remove_all(rule, pattern = "[<]|[{]|[}]|[>]")
      ) %>%
    separate(
      rule,
      into = c("lhs", "rhs"),
      sep = " = "
      ) %>%

@@

  # Confidence and Lift by hand
  group_by(
    lhs,
    rhs_course
    ) %>%
  mutate(
    lhs.rhsTake.support = sum(support) # Proba of lhs and taking rhs course
    ) %>%
  ungroup %>%

@@

  # Confidence and Lift
  mutate(
    rhs.taken = str_detect(rhs, "fail|pass")
    ) %>%
  group_by(
    lhs,
    rhs_course
    ) %>%
    mutate(
    lhs.rhsTake.support = sum(support * rhs.taken) # Proba of lhs and taking rhs course
    ) %>%
  ungroup %>%

@@

  # Confidence and lift
  group_by(
    lhs, 
    rhs_course
    ) %>%
  mutate(
    lhs.rhsTake.support = max(support),
    confidence          = support / lhs.rhsTake.support,
    lift                = confidence / rhs.support
    ) %>%
  ungroup %>%

@@

### Editing AR
```{r edit_AR}
edit_AR <- function(AR){

@@

    select(
      lhs, rhs,
      support, count,
      confidence, rhs.support,
      lift, 
      everything(),
      - matches("rate|course|grade|outcome|taken")
    ) %>%

@@

AR <- lapply(
  X   = AR,
  FUN = edit_AR
  )
```

@@

# Remove objects
rm(
  my_apriori, clean_AR, compute_metrics, edit_AR, make_AR,
  AR, transaction
  )
```

@@

    ruleInduction(
      confidence = 0,
      control    = list(verbose = FALSE)
      )

@@

### Editing SR
```{r SR edit}
    mutate_at(
      c("support",
        "confidence", "lift"),
      funs(round(., 5))
    ) %>%
    filter(!`LHS Course ID`==`RHS Course ID`) %>%
    select(-`LHS Course ID`, -`LHS Quality`, -`RHS Course ID`, -`RHS Quality`)
```

>>>>

    # separate rule
    mutate(
      rules = str_remove_all(rules, pattern = "[<]|[{]|[}]|[>]")
      ) %>%
    separate(
      rules,
      into = c("lhs", "rhs"),
      sep = " = "
      ) %>%

@@

  # Confidence and Lift by hand
  group_by(
    lhs,
    rhs_course
    ) %>%
  mutate(
    lhs.rhsTake.support = sum(support), # Proba of lhs and taking rhs course
    lhs.rhsTake.count   = lhs.rhsTake.support * n_students
    ) %>%
  ungroup %>%

@@

  # Confidence and Lift
  mutate(
    rhs.taken = str_detect(rhs, "fail|pass")
    ) %>%
  group_by(
    lhs,
    rhs_course
    ) %>%
    mutate(
    lhs.rhsTake.support = sum(support * rhs.taken), # Proba of lhs and taking rhs course
    lhs.rhsTake.count   = lhs.rhsTake.support * n_students
    ) %>%
  ungroup %>%

@@

  # Confidence and lift
  group_by(
    lhs, 
    rhs_course
    ) %>%
  mutate(
    lhs.rhsTake.support = max(support),
    lhs.rhsTake.count   = lhs.rhsTake.support * n_students,
    confidence          = support / lhs.rhsTake.support,
    lift                = confidence / rhs.support
    ) %>%
  ungroup %>%

@@

### Editing AR
```{r edit_AR}
edit_rules <- function(AR){

@@

    select(
      lhs       , rhs,
      support   , count,
      confidence, rhs.support,
      lift,
      matches("rhsTake")
    ) %>%

@@

AR <- lapply(
  X   = AR,
  FUN = edit_rules
  )
```

@@

# Remove objects
rm(
  my_apriori, make_AR,
  AR, transaction
  )
```

@@

    ruleInduction(

      # keep all subsequences
      confidence = 0,

      control    = list(verbose = FALSE)

@@

### Editing SR
```{r SR edit}
SR <- lapply(
  X   = SR,
  FUN = edit_rules
  )
```
